The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-10 paper/ms.tex
typo in acknowledgement

BP acknowledges being on the traditional territory of the Lenape Nations and, today, we grecognize that Manhattan continues to be the home to many Algonkian peoples. We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University. BP and TW would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.

>>>>

BP acknowledges being on the traditional territory of the Lenape Nations and, today, we recognize that Manhattan continues to be the home to many Algonkian peoples. We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University. BP and TW would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
